---
title: "ELISR_template_1plate"
author: "Matthew Snelson"
date: "21/04/2020"
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
    theme: journal
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '..')  # set root-dir. assumes script is in a script directory.

library(devtools)
install_github("mattsnelson/handytools") #load ELISR package

library(here)
library(tidyverse)
library(ggpubr)
library(DT)
library(drc)       # for 4pl sigmodial calcs
```

# Overview

Instructions for using this template:
- This is designed to be used with one plate only (have other templates for combining 2,3 or more plates)
- Fill out the info required in the data-import section


Experiment Conducted on XXXXXX

This report compiled: `r Sys.time()`

Kit: [R&D](https://www.rndsystems.com/products/mouse-cystatin-c-duoset-elisa_dy1238)

Sample Dilution: 1:1200

Standard concentrations in pg/mL

Copmleted as per manufacturers instructions. Note only used TMB as substrate (rather than a 1:1 mic of TMB and H2O2 as they recommend; that doesn't work)


# Data Import

The handytools::elisr package requires the following things:
- plate template (96 well format)
      - with S1,S2, etc for the standards
      - the blank (e.g. "BLK")
      - sample ID (use path numbers)
- plate data (96 well format)

Additionally this workflow requires to input:
- the concentrations of the standards.
- the dilution factor
- metadata table

```{r dataimport, mesage=FALSE}
# plate 1 repeat as required
plate1_template <- readxl::read_xlsx(path=here("data/cys-c", "cys_c_plate_template.xlsx"), range = "B2:M10")
plate1_data <- readxl::read_xlsx(path=here("data/cys-c/data-raw", "gpr43_cys-c_plate1.xlsx"), range = "B15:M23")  # range B15:M23 on clariostar output

#plate 2
plate2_template <- readxl::read_xlsx(path=here("data/cys-c", "cys_c_plate_template.xlsx"), range = "B21:M29")
plate2_data <- readxl::read_xlsx(path=here("data/cys-c/data-raw", "gpr43_cys-c_plate2.xlsx"), range = "B15:M23")  # range B15:M23 on clariostar output


# specify Blank
blank = "BLK"

# specify concentrations of the standards
stds <- data.frame(ID=c(     "S1",  "S2",   "S3",  "S4",    "S5",     "S6",    "S7"),
                   conc=c(     1000,     500,    250,  125,   62.5,   31.25,   15.6))

# dilution factor
dil <- 1200

# metadata
metadata <- read_csv(file="data/metadata/gpr43-metadata.csv")

#write_path = where would like results outputted to 
write_path <- "data/cys-c/data/cys_c_results.csv"

```

# Raw Data

## Standards Concentration
```{r}
DT::datatable(stds)

```


## Plate 1 - Raw Data
This is the raw OD data (inputted from excel) and the plate template:
```{r}
DT::datatable(plate1_template)

DT::datatable(plate1_data)

```

# Analysis - Plate 1

## Interpolation

This uses my elisr function to manipulate data and then uses the drc package to fit to a 4 point sigmoidal curve.

```{r plate1, message = FALSE, warning=FALSE}
##Plate 1 Anlaysis
plate1_output <- handytools::elisr(plate1_template, plate1_data, blank)
colnames(plate1_output)[1] <- "ID"

plate1_stds <- merge(stds, plate1_output, by= "ID", all.x=T, all.y=F) 

plate1_model<-drm(mean_OD_minus_blank~conc,
            fct=LL.4(names=c("Slope", "Lower", "Upper", "ED50")),
            data=plate1_stds)  #creates 4PL model
plot(plate1_model)

plate1_resp <- plate1_output$mean_OD_minus_blank # values of samples here.

plate1_results <-ED(plate1_model,plate1_resp,type="absolute",display=F)
plate1_results <- as.data.frame(plate1_results)

plate1_output[length(plate1_output)+1] <- plate1_results[1]
plate1_output$plate <- "1"

# multiply estimate by DIL factor to get concencentration
plate1_output <- plate1_output %>%
  mutate(sample_conc = Estimate * dil)

# Round SD, CV% and Estimate (for easy reading)
plate1_output$SD <- round(plate1_output$SD, 5)
plate1_output$CV_percent <- round(plate1_output$CV_percent, 2)
plate1_output$Estimate <- round(plate1_output$Estimate, 4)
plate1_output$sample_conc <- round(plate1_output$sample_conc, 4)

DT::datatable(plate1_output)
```
NB: "Estimate" (last column) is the concentration of the diluted sample.
    "sampe_conc" = the sample concentration (the Estimate multiplied by the dilution factor)

## Merge - Plate 1

Merges with metadata to allow for graphing

```{r plate1_merge}
plate1_results <- plate1_output

colnames(plate1_results)[1] <- "path"
plate1_results <- merge(plate1_results, metadata, by = "path", all.x = TRUE, all.y = FALSE)

DT::datatable(plate1_results)
```


## Graph:

Graph Results

```{r plate1_graph}
ggplot(plate1_results, aes(x = group, y = sample_conc)) +
  geom_boxplot(aes(fill = group)) + 
    scale_fill_brewer(palette="Dark2") + 
    labs(title="Experiment",x="Group", y = "Sample Concentration") + 
    theme_minimal() + 
    theme(axis.text.x = element_text(angle=90, hjust=1))


write_csv(plate1_results, path = write_path)
```

Write results to: `r write_path`

# SessionInfo

```{r sessinfo}
session_info()
```
